---
title: "PoW M&M Cleaning"
author: "Rory Denham"
date: "5 June 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

#Load Libraries ------------------------
library(officer)
library(magrittr)
library(tidyverse)
library(flextable)
library(janitor)
library(lubridate)
library(scales)
library(stringr)
library(tibble)
library(knitr)
library(kableExtra)
library(plotly)
library(explorers)
```

## M&M Datacleaning

The R Markdown file is designed to check the **M&M Historical Data** component of the M&M reports. As a rule the aim is for errors to be removed as data is entered into the CTS database, however this script serves as a systematic double check to ensure all data has been enetered correctly at the end of the month.

```{r DataImport and Datatypes}

#Load Data ------------------------------------

#####
#change this file accordingly >>>>D:/M&M_Query_Data/ "insert pathfile here"

#PathFile <- "D:M&M_Query_Data_Laura/Oct_Nov/"
Pathfile <- "C:\\Users\\Break\\Desktop\\MM_Jan_2019_Data\\Historical\\"

#####

#change to use readr package - require downloading the package first
MM.Inf <-       read_csv(file = paste(Pathfile, "qry_Historical_Inf.csv", sep = ""), 
                         col_types = cols(OpDate = col_date()
                                          )
                         )
MM.Pres_Main <- read_csv(file = paste(Pathfile, "qry_Historical_Main.csv", sep = ""))
                         # col_types = cols(OpDate = col_date(format = "%d/%m/%Y"),
                         #                  AdmDate = col_date()
                         #                  )
                         )
MM.ReAdm <-     read_csv(file = paste(Pathfile, "qry_Historical_ReAdm.csv", sep = ""))
MM.RTT <-       read_csv(file = paste(Pathfile, "qry_Historical_RTT.csv", sep = ""))

#Data cleaning and wrangling ------------------

####Fix Variable formats####

str(MM.Pres_Main)
MM.Pres_Main$AdmDate <- as.Date(MM.Pres_Main$AdmDate, "%d/%m/%Y")
MM.Pres_Main$ConsultDate <- as.Date(MM.Pres_Main$ConsultDate, "%d/%m/%Y")
MM.Pres_Main$OpDate <- as.Date(MM.Pres_Main$OpDate, "%d/%m/%Y")
MM.Pres_Main$DischargeDate <- as.Date(MM.Pres_Main$DischargeDate, "%d/%m/%Y")
MM.Pres_Main$PO_ICUAdmDt <- as.Date(MM.Pres_Main$PO_ICUAdmDt, "%d/%m/%Y")
MM.Pres_Main$PO_ICUOutDt <- as.Date(MM.Pres_Main$PO_ICUOutDt, "%d/%m/%Y")
MM.Pres_Main$PO_RFWDt <- as.Date(MM.Pres_Main$PO_RFWDt, "%d/%m/%Y")
MM.Pres_Main$PO_ExtbDt <- as.Date(MM.Pres_Main$PO_ExtbDt, "%d/%m/%Y")
MM.Pres_Main$PreOp_Comments <- as.character(MM.Pres_Main$PreOp_Comments)
MM.Pres_Main$PO_Comments <- as.character(MM.Pres_Main$PO_Comments)


MM.Pres_Main$OpCategory <- factor(MM.Pres_Main$OpCategory, levels = (c("CABG",
                                                                       "CABG/Other",
                                                                       "Valve",
                                                                       "Valve/Other",
                                                                       "CABG/Valve",
                                                                       "CABG/Valve/Other",
                                                                       "Other")))


MM.Inf$OpDate <- as.Date(MM.Inf$OpDate, "%d/%m/%Y")
MM.ReAdm$OpDate <- format(as.Date(MM.ReAdm$OpDate, "%d/%m/%Y"), "%d/%m/%Y")
MM.RTT$OpDate <- as.Date(MM.RTT$OpDate, "%d/%m/%Y")

#create date number variable
MM.Pres_Main$Num_Months <- month(MM.Pres_Main$OpDate) - month(min(MM.Pres_Main$OpDate)) + 1
MM.Inf$Num_Months <- month(MM.Inf$OpDate) - month(min(MM.Inf$OpDate)) + 1

#add month variable
MM.Pres_Main %<>% mutate(Month = month(OpDate, label = TRUE, abbr = FALSE))
MM.Inf %<>% mutate(Month = month(OpDate, label = TRUE, abbr = FALSE)) 

MM.Pres_Main %<>% mutate(`PO_Vent>24hr` = if_else(PO_ICUAdmDt-PO_ExtbDt>=1, 1, 0))

#add the total caseload (per month) to inf table
monthtotals <- MM.Pres_Main %>%
  group_by(Month) %>% 
  summarise(Total = n()) %>% 
  arrange(Month) %>% 
  select(Month, Total)

if(nrow(MM.Inf) != 0) {
  MM.Inf %<>% group_by(`Patient Details`) %>% 
    mutate(TotalCasesMonthly = if_else(Num_Months == 1, monthtotals[[1, 2]], monthtotals[[2, 2]]))
}

```

## Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
IcuTimelineData <- MM.Pres_Main


IcuTimelineData[IcuTimelineData$Pt_LName == 'NEAL, H',"DischargeDate"] = as.Date('2019-02-07')
IcuTimelineData[IcuTimelineData$Pt_LName == 'LOVETT, S',"AdmDate"] = as.Date('2019-01-01')

IcuTimelineData %<>% mutate(Pt_LName = paste(OpDescription, " (", AdmConsultantInitials, ") ", Pt_LName))

IcuTimelineData$Pt_LName <- factor(IcuTimelineData$Pt_LName, levels = (IcuTimelineData$Pt_LName[order(IcuTimelineData$OpDate)]))

Min.Date <- min(MM.Pres_Main$AdmDate, na.rm = T)
Max.Date <- max(MM.Pres_Main$DischargeDate, na.rm = T)

weekenddates <- seq(as.Date(Min.Date),as.Date(Max.Date),by = 1)
weekenddates <- weekenddates[weekdays(weekenddates) %in% c('Saturday','Sunday')]

#weekend highlight function
# test <- data.frame(DATE=seq(from = min(IcuTimelineData$AdmDate),
#                             to = max(IcuTimelineData$DischargeDate),
#                             by = "day"))
# 
# test$weekend <- weekdays(test$DATE) %in% c("Saturday", "Sunday")
# test %<>% filter(weekend == T)
# 
#   geom_segment(data = test, aes(x=DATE, xend = DATE+2, y = -Inf, yend = Inf), fill="yellow") +

TimelinePlot <- ggplot(IcuTimelineData, aes(y = Pt_LName)) +
  # geom_hline(aes(yintercept = Pt_LName, colour = OpConsultant)) +
  geom_vline(xintercept = weekenddates, alpha =0.2, size = 5) +
  geom_segment(aes(x = AdmDate, xend = DischargeDate, y = Pt_LName, yend = Pt_LName, linetype = "Total Stay"), colour = "#000000") + #total stay duration (black)
  geom_segment(aes(x = PO_ICUAdmDt, xend = PO_ICUOutDt, y = Pt_LName, yend = Pt_LName, linetype = "ICU Bed Block Duration"), size = 5, colour = "#D10202") + #total ICU stay - effectively displays bed block (red)
  geom_segment(aes(x = PO_ICUAdmDt, xend = PO_RFWDt, y = Pt_LName, yend = Pt_LName, linetype='ICU Stay (Ready for Discharge)'), size = 5, colour = "#D16103") + #ICU stay until ready for discharge(orange)
  geom_segment(aes(x = OpDate, xend = OpDate + 0.5, y = Pt_LName, yend = Pt_LName, linetype = "Operation"), colour = "#4E84C4", size = 5) + 
  geom_segment(aes(x = AdmDate, xend = AdmDate + 0.1, y = Pt_LName, yend = Pt_LName), size = 5, show.legend = TRUE) +
  geom_segment(aes(x = DischargeDate, xend =DischargeDate+0.1, y = Pt_LName, yend = Pt_LName), size = 5) +
  scale_x_date(date_breaks = "3 days", labels = date_format("%d\n%b"), date_minor_breaks = "1 day") +
  scale_linetype_manual(name = "", values = c(1, 1, 1, 1), 
                        guide = guide_legend(override.aes = list(color = c("#D10202", "#D16103", "#4E84C4", "#000000")))) +
  # facet_wrap(~Month, scales = "free_y") +
  labs(caption = "*x-axis major ticks =  3 day intervals \n *x-axis minor ticks = 1 day intervals \n *Weekends highlighted in grey") +
  theme_minimal() +
  theme(axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        axis.line = element_line(colour = "#000000", size = 1, linetype = "solid"),
        panel.grid.major.y = element_blank(),
        legend.position = "bottom", 
        legend.title = element_blank())


ggplotly(TimelinePlot)
# "Admission Duration"
# , "Admission Duration" = "#000000"
#add consultant and patient names or highlight with colour coding
#add weekends in gray background
#add infection dates
#highlight deaths
#show bed block as darker red for the ICU segments
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
